|

### 2019-10-23 analysis/paper/cover_letter.Rmd
Draft a new cover letter

@@

Professor Paul J B Hart  
Fish and Fisheries  
Department of Biology  
University of Leicester  
University Road  
Leicester  
LE1 7RH, UK

Dr. Hart,

We thank you for taking the time to examine our initial idea for our paper "Improving the communication and accessibility of stock assessment using interactive visualization tools". Based on your feedback, we have assembled a paper we feel fits the theme of Ghoti papers, and points towards ways of improving the stock assessment process. We re-iterate that this paper is not technical in nature, but mostly to encourage readers to pursue investigating these interactive visualization tools, and to convince readers that these tools are very much accessible to practicing biologists.

I look forward to your decision.

>>>>

Howard I. Browman, Ph.D.  
Editor-in-Chief  
ICES Journal of Marine Science  
Institute of Marine Research  
Marine Ecosystem Acoustics Group  
Austevoll Research Station  
5392 Storebø  
Norway

@@

Dr. Browman,

I am writing to submit our manuscript entitled, **"Improving the communication and accessibility of stock assessment using interactive visualization tools"** for consideration as a **_Quo Vadimus_** article in **ICES Journal of Marine Science**. In our manuscript, we discuss the merits of applying modern interactive visualization tools to stock assessment processes and we hope to convince readers that these tools, which we use every day on a range of web sites, are very accessible to practicing biologists. We argue that the application of these tools alleviates some of the difficulty in presenting the mass of information produced by complex monitoring programs and statistical models to end-users in a meaningful, interactive and engaging way. To exemplify this point, we describe the structure of three interactive dashboards developed to aid the exploration and communication of results from 1) a fishery-independent trawl survey, 2) a mark-recapture tagging program, and 3) a stock assessment model. In each case we discuss the efficacy of applying such tools in a stock assessment context and contrast this approach with more traditional modes of communicating the results from complex monitoring programs and stock assessment models.

We believe that this is a fitting and timely article for the Journal's **_Quo Vadimus_** type as there are a growing number of scientists from a wide range of disciplines applying these tools to explore and communicate their results. We can personally attest that the application of interactive tools has helped us in our daily work and we hope that our perspective will appeal to readers of **ICES Journal of Marine Science** and encourage the application of interactive tools.

We look forward to your decision.
